A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-04-19 paper/ms.tex
Fix latex mistakes and add binary-single discussion

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\usepackage{tikz}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\sunanalog}{\ensuretext{HD HD 240429}}
\newcommand{\bizarrone}{\ensuretext{HD 240430}}

@@

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
obtained high resolution spectroscopy for both \sunanalog\ and \bizarreone\.
\todo{from where? mention briefly Keck HIRES}
The resulting measurements from this effort include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:t2}.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
  \end{center}
  \caption{%
    Differences in posterior samples over Galactocentric phase-space coordinates
    for the two stars \sunanalog\ and \bizarreone\.
    \label{fig:dxdv}}
\end{figure}

@@

% binary-single and binary-binary exchange
Another scenario that two unrelated stars may end up in a wide binary system
is multi-body gravitational scattering.
We consider the exchange probabilities in binary-single and binary-binary interactions.
Given their low binding energy compared to incoming velocity of field stars,
this is low.
Two factors that make this even more unlikely are that both stars are very young given their large Li,
and that if the pair is a result of scattering, one expect to end up with typical stars of the field,
not HD30 with anomalous abundance patterns.

>>>>

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\sunanalog}{\text{HD 240429}}
\newcommand{\bizarreone}{\text{HD 240430}}

@@

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
obtained high resolution spectroscopy for both \sunanalog\ and \bizarreone.
\todo{from where? mention briefly Keck HIRES}
The resulting measurements from this effort include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:t2}.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
  \end{center}
  \caption{%
    Differences in posterior samples over Galactocentric phase-space coordinates
    for the two stars \sunanalog\ and \bizarreone.
    \label{fig:dxdv}}
\end{figure}

@@

% binary-single and binary-binary exchange
Two stars unrelated at birth may end up in a binary system via binary-single scattering event
that results in an exchange of binary member.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The exchange rate for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
\end{eqnarray}
where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
\end{eqnarray}
when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
which is appropriate for wide binaries scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars with constant $n=1$~pc$^{-3}$,
and the incoming velocity is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
stars in any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^3} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
\end{eqnarray}
low enough to be negligible.

In regions where binarity fraction is high, binary-binary scattering may be more important
than binary-single scattering (\todo{CITE})

%Two factors that make this even more unlikely are that both stars are very young given their large Li,
%and that if the pair is a result of scattering, one expect to end up with typical stars of the field,
%not HD30 with anomalous abundance patterns.
